Simulations of Ballot Polling Risk-Limiting Audits

### 2022-10-12 providence/sections/adversary.tex
typo

To illustrate the practical implication of this property, we consider a toy example: an RLA of a two-candidate contest with margin $1\%$ and risk limit $10\%$. 
Suppose we would like to achieve a $0.9$ conditional stopping probability in each round of the audit. For \Providence, we can compute a new round size for each round based on the previous samples, but for \Minerva we need to commit to a round schedule in advance. So for \Minerva we choose a first round size which gives a $0.9$ probability of stopping, and then we set the subsequent marginal round sizes to be $1.5$ times each previous round size. This multiplier of $1.5$ is known to give a probability of stopping roughly $0.9$ in the second round if the first round size has probability of stopping $0.9$. Audit software ARLO, used by many states, commits to this round schedule by default. Both audits therefore begin with first round size of $17,272$ to give a $0.9$ probability of stopping, and both will stop in the first round if the sample contains at least $8,725$ ballots for the winner. We now consider two cases for which the audit proceeds to a second round.

In one case there are $8,724$ votes for the winner in the sample, just one fewer than the minimum needed to meet the risk limit. In the \Minerva audit, we are already committed to a second round size of $43,180$ which, given the nearly-passing sample of the first round is higher than necessary, achieving a stopping probability in the second round of $95.4\%$. The \Providence audit samples more than $9,000$ fewer ballots with a round size of $34,078$, achieving the desired $0.9$ probability of stopping.

In a less lucky sample, the winner recieves $8,637$ ballots, few more than the loser recieves. In the \Minerva audit, we again have to use a second round size of $43,180$, but now this round size only achieves a $72.7\%$ probability of stopping, significantly less than the desired $0.9$. Again, the \Providence audit can scale up the second round size according to the first sample and achieve the desired $0.9$ probability of stopping with $58,007$ ballots.

>>>>

To illustrate the practical implication of this property, we consider a toy example: an RLA of a two-candidate contest with margin $1\%$ and risk limit $10\%$. 
Suppose we wish to achieve a conditional stopping probability $0.9$ in each round of the audit. For \Providence, we can compute a new round size for each round based on the previous samples, but for \Minerva we need to commit to a round schedule in advance. So for \Minerva we choose a first round size which gives a $0.9$ probability of stopping, and then we set the subsequent marginal round sizes to be $1.5$ times each previous round size. This multiplier of $1.5$ is known to give a probability of stopping roughly $0.9$ in the second round if the first round size has probability of stopping $0.9$. Audit software ARLO, used by many states, commits to this round schedule by default. Both audits therefore begin with first round size of $17,272$ to give a $0.9$ probability of stopping, and both will stop in the first round if the sample contains at least $8,725$ ballots for the winner. We now consider two cases for which the audit proceeds to a second round.

In one case there are $8,724$ votes for the winner in the sample, just one fewer than the minimum needed to meet the risk limit. In the \Minerva audit, we are already committed to a second round size of $43,180$ which, given the nearly-passing sample of the first round is higher than necessary, achieving a stopping probability in the second round of $.954$. The \Providence audit samples more than $9,000$ fewer ballots with a round size of $34,078$, achieving the desired $0.9$ probability of stopping.

In a less lucky sample, the winner recieves $8,637$ ballots, few more than the loser recieves. In the \Minerva audit, we again have to use a second round size of $43,180$, but now this round size only achieves a $0.727$ probability of stopping, significantly less than the desired $0.9$. Again, the \Providence audit can scale up the second round size according to the first sample and achieve the desired $0.9$ probability of stopping with $58,007$ ballots.
